\bf Faster Neural Machine Translation Inference

### 2018-02-04 fast-beam/fast-beam.tex
fast beam paper

Using both the fused kernel and top-up batching to translate

>>>>

Using both the fused kernel and top-up batching to translate led to a cummalative speed improvement of up to 57\% and 34\% for the OpenSubtitles and Europarl test set, respectively, when no maxi-batching is used, Figure~\ref{fig:cummulative-europarl} and Figure~\ref{fig:cummulative-opensubtitles}. With maxi-batching, the speed was up to 41\% and 21\%.

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{cummulative-europarl.png}} 
\end{tabular}
\caption{Cummulative results (Europarl}
\label{fig:cummulative-europarl}
\end{figure}

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{cummulative-opensubtitles.png}} 
\end{tabular}
\caption{Cummulative results (OpenSubtitles}
\label{fig:cummulative-opensubtitles}
\end{figure}
